The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population

### 2017-04-07 repeater-vladata.tex
worked through paul s, geoff b, laura s comments

\title{The \frb\ Campaign, a Multi-Telescope Burst Detection, and Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
We present results of the coordinated observing campaign that made the first localization of a Fast Radio Burst, FRB 121102. Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz. We use multi-observatory detection and constraints with modeling of bursts only seen at 3~GHz to show that burst spectra are not well characterized by a powerlaw. Instead, bursts typically have a $\sim500$~MHz-scale envelope in which the apparent radio energy emitted is as high as $10^{40}$\ erg. The dispersion measure apparently changes significantly between bursts, which suggests that they have intrinsic spectral structure that can bias the estimate of DM by as much as 5 pc cm$^{-3}$. We use \frb\ as a prototype of the FRB class to estimate a volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1. This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
\end{abstract}

@@

Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[the ``Lorimer burst'';][]{2007Sci...318..777L}. Their large dispersion measures (DM) implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec. Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01\arcsec \citep[$\sim40$\ pc]{OPT, EVN}.

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the Lorimer burst.

Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. Its coincidence with a compact, persistent radio source is consistent with \frb\ as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb\ is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}. It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments \citep{2014ApJ...787..138L}.

@@

\includegraphics[width=2\columnwidth]{timeline}
\caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns. Symbols show days with observations with letters L, S, C, K referring to radio frequencies of 1.4, 3, 4.5, and 12~GHz, respectively. Circles highlight observations that detected bursts from \frb. Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session. The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes. The solid black line shows the simultaneous burst detection at VLA and Arecibo.
\label{fig:sched}}
\end{center}
\end{figure*}

@@

The \frb\ observing campaign started in late 2015 with a 10~hr campaign ($\sim1$~hr per session) observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign ($\sim2$~hr per session) at 3~GHz in the C and CnB configurations in coordination with Arecibo \citep{2016arXiv160308880S}. We concluded with a 40~hr, coordinated campaign ($\sim2$~hr per session) from August through September 2016 in the B configuration and during the move to the most extended A configuration. In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which includes all nine burst detections and is the widest bandwidth to have ever detected an FRB.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The channel frequency width was set to maximize sensitivity to the known DM of \frb\ with the largest total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each.

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}. Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}. Gain calibration was made from observations of J0555+3948 by the telcal system, which uses phase-only calibration. A flux scale is calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.

@@

We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al. 2008) for 3 hours each on four epochs starting at MJDs 57643, 57645, 57648, and 57649. Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time. The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes. The AMI-LA data were binned to eight 0.625~GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}. Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.

We inspected the calibrated visibilities, and did not find any signal above 30 mJy in the 1s samples at and in the vicinity of the detected bursts. Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location. Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger. We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy. Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB. This limit is similar to the flux density measured by the VLA \citep{LOC}.

@@

Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage. The burst on 17 Sep 2016 was detected with Arecibo and the VLA with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy, respectively. Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not consistent with a powerlaw model for the burst spectra. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+3.7$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-0.4$. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a powerlaw model is inappropriate even for a single burst.

@@

\subsection{VLA Bursts}

\begin{figure*}[htb]
\begin{center}
 \includegraphics[width=1.9\columnwidth]{aovla_spec.png}
 \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories. Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$. The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz). The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
 \label{fig:sgram}}
\end{center}
\end{figure*}

\subsubsection{Spectral Modeling}
\label{sec:spec}

This paper refines the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways. We use a better calibration scheme and have optimized the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.

@@

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{cc|ccc|cccccc}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observered properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
(2016)       &  (MJD)     &           & (mJy) 			& (mJy) 		& (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194				& +3			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
2 Sep & 57633.67986367      & 179 		& 1500				& --35 			& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
2 Sep\tablenotemark{a} & 57633.69515938 & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
7 Sep & 57638.49937435      & 12 		& 55				& +5 			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
12 Sep & 57643.45730263      & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
14 Sep & 57645.42958602      & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
15 Sep\tablenotemark{a} & 57646.46600650 & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
17 Sep\tablenotemark{b} & 57648.43691490 & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
18 Sep & 57649.45175697      & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

Figure \ref{fig:spec} shows that the Stokes I spectra are generally characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%. To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}. MCMC sampling requires a generative model for the data, so we wrote functions in Python to create 2d dynamic spectra. The dynamic spectra are generated in the spectral domain as a Gaussian envelope (with amplitude, center, and width) and in the temporal domain by a start time, temporal width, and DM. We assume a dispersive delay that scales as frequency squared.

The 6-dimensional models were sampled with 100 walkers taking 500 steps. Typically, the first 200 steps were used to burn in the walkers and were ignored. A flat prior was used over all ranges with valid data. An additional requirement was that the integrated burst signal must have a detection significance higher than 8$\sigma$. The inter-channel modulation (scintillation) was ignored in the model. The measured, off-burst noise value was typically 70 mJy per 5~ms integration and 4~MHz channel.

@@

\begin{figure*}[ht]
\begin{center}
 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57623.png}
  \includegraphics[width=0.33\columnwidth]{spec_57633_scan7.png}
  \includegraphics[width=0.33\columnwidth]{spec_57633_scan13.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57638.png}
  \includegraphics[width=0.33\columnwidth]{spec_57643.png}
  \includegraphics[width=0.33\columnwidth]{spec_57645.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57646.png}
  \includegraphics[width=0.33\columnwidth]{spec_57648.png}
  \includegraphics[width=0.33\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz. Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. The solid line is a best-fit Gaussian model found through MCMC modeling. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
\label{fig:spec}}
\end{center}
\end{figure*}

@@

While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier. Figure \ref{fig:corner} shows the scatterplot matrix for the MCMC run on burst 57646 \citep{corner}. Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM. The model seems to be too simple for this burst or that it can be decomposed into two bursts.

@@

\caption{(Top) DM as a function of time for nine 3~GHz bursts detected by the VLA. The 95\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz. (Bottom) Burst DM versus temporal width for all nine VLA bursts.
\label{fig:dmmodel}}
\end{center}
\end{figure}

>>>>

\title{The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
We present results of the coordinated observing campaign that made the first arcsecond localization of a Fast Radio Burst, FRB 121102. Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz. We use multi-observatory detection and constraints with modeling of bursts only seen at 3~GHz to show that burst spectra are not well characterized by a powerlaw. Instead, bursts typically have a $\sim500$~MHz-scale envelope in which the apparent radio energy emitted is as high as $10^{40}$\ erg. The dispersion measure apparently changes significantly between bursts, which suggests that they have spectral structure that can bias the estimate of DM by as much as 5 pc cm$^{-3}$. We use \frb\ as a prototype of the FRB class to estimate a volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1. This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
\end{abstract}

@@

Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep{2007Sci...318..777L}. There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order 2~ms. Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}. Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec. Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a $z=0.193$\ with a precision of 0.01\arcsec\ \citep[$\sim40$\ pc]{OPT, EVN}.

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the first FRB detection.

Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, observations do not strongly constrain these models. The coincidence of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively). It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.

@@

\includegraphics[width=2\columnwidth]{timeline}
\caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns. Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 12~GHz, respectively. Circles highlight observations that detected bursts from \frb. Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session. The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes. The solid black line shows the simultaneous burst detection at VLA and Arecibo.
\label{fig:sched}}
\end{center}
\end{figure*}

@@

The \frb\ observing campaign started in November 2015 with a 10~hr campaign ($\sim1$~hr per session) observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign ($\sim2$~hr per session) at 3~GHz in the C and CnB configurations in coordination with Arecibo \citep{2016arXiv160308880S}. We concluded with a 40~hr, coordinated campaign ($\sim2$~hr per session) from August through September 2016 in the B configuration and during the move to the most extended A configuration. In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which includes all nine burst detections and is the widest bandwidth to have ever detected an FRB.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The channel frequency width was set to maximize sensitivity to the known DM of \frb\ with the largest total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each and had sensitivity of 5~mJy in 5~ms ($1\sigma$).

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}. Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}. Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration. A flux scale is calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.

@@

We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al. 2008) for 3 hours each on four epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649. Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time. The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes. The AMI-LA data were binned to eight 0.625~GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}. Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.

We inspected the calibrated visibilities, and did not find any signal above 30 mJy in the 1s samples at and in the vicinity of the detected bursts. This corresponds to a sensitivity of 15~Jy for an assumed pulse width of 2~ms. Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location. Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger. We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy. Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB. This limit is similar to the flux density measured by the VLA for the persistent source \citep{LOC}.

@@

\begin{figure}[htb]
\begin{center}
 \includegraphics[width=\columnwidth]{aovla_spec.png}
 \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories. Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$. The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz) and flagged data is grey. The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
 \label{fig:sgram}}
\end{center}
\end{figure}

**integrated flux is assuming 5 ms width!**

**confirm arecibo integrated flux and sensitivity**

Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage. The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively. The VLA integration time of 5~ms underresolves the pulse and the true integrated flux density would be 280 mJy for an assumed pulse width of 2~ms.
% correct the followign for estimated integrated flux
Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not consistent with a powerlaw model for the burst spectra. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+3.7$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-0.4$. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a powerlaw model is inappropriate even for a single burst.
% could note that these limits are understated by VLA integrated flux underestimate

@@

\subsection{VLA Bursts}
\subsubsection{Spectral Modeling}
\label{sec:spec}

This paper refines the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways. We use a better calibration scheme and have optimized the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[RA, Dec $=$ 05h31m58.70s, +33d08m52.5s;][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.

@@

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{cc|ccc|cccccc}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observered properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & Image S/N & $S_{\rm{I,int}}$	& $S_{\rm{V}}$ 	& DM 	& dt 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
(2016)       &  (MJD)     &           & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\	
17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
\tablenotetext{b}{Detected simultaneously with Arecibo.}
\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\label{tab:spec}
\end{table*}

Figure \ref{fig:spec} shows that the Stokes I spectra are generally characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%. Diffractive scintillation from the Milky Way has a typical bandwidth of 7~MHz along this line of sight \citep{2002astro.ph..7156C}, which is similar to the channel size of 4~MHz.

To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}. We modeled the dynamic spectra with a broad gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a temporal width. The 6-dimensional models were sampled with 100 walkers taking 500 steps; we ignored the first 200 steps to allow the walkers to properly sample the posterior distributions. A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$. The inter-channel modulation (scintillation) was ignored in the model. The measured, off-burst noise value was typically 70 mJy per 5~ms integration and 4~MHz channel.

@@

\begin{figure*}[ht]
\begin{center}
 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.5\columnwidth]{spec_57623.png}
  \includegraphics[width=0.5\columnwidth]{spec_57633_scan7.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.5\columnwidth]{spec_57633_scan13.png}
  \includegraphics[width=0.5\columnwidth]{spec_57638.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.5\columnwidth]{spec_57643.png}
  \includegraphics[width=0.5\columnwidth]{spec_57645.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.5\columnwidth]{spec_57646.png}
  \includegraphics[width=0.5\columnwidth]{spec_57648.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.5\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz. Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. The solid line is a best-fit Gaussian model found through MCMC modeling. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
\label{fig:spec}}
\end{center}
\end{figure*}

@@

While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier. Figure \ref{fig:corner} shows the scatter plot matrix \citep{corner} for the MCMC run on burst 57646. Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM. Assuming that the model is appropriate, this implies that it can be decomposed into two bursts.

@@

\caption{(Top) DM as a function of time for nine 3~GHz bursts detected by the VLA. The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz. (Bottom) Burst DM versus temporal width for all nine VLA bursts.
\label{fig:dmmodel}}
\end{center}
\end{figure}
